---
title: "Biological control"
author: "Jorge Isla Escudero"
date: "9 de diciembre de 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data imput

```{r data}
#
bi <-read.table("../data/bractocera_intensity.csv", header=TRUE, sep=";", dec=".",na.strings="NA",comment.char = "#")

str(bi)

```
### meaning of the variables

finca: finca
habitat: PRO/IMP
time: nº exposition days
landscape: landscape complexity of the 'finca' 
removal: nº of false larvas disappeared 
rain:-
max: 4 larve disponible, minus the larvae that could not be revised because the offer was damaged. For example, if one of the plates has disappeared and only 2/4 larvae can be checked, max = 2.

### Removal distributions

```{r freqdistrib, echo=T}

# Compute a histogram of `removal`
require(ggplot2)
ggplot(data=bi, aes(removal/max)) + geom_histogram()

ggplot(bi, aes(removal/max, fill = finca)) + geom_histogram(alpha = 0.5)
ggplot(bi, aes(removal/max, fill = habitat)) + geom_histogram(alpha = 0.5)
ggplot(bi, aes(removal/max, fill = landscape)) + geom_histogram(alpha = 0.5)

```

### Complete Bractocera false larves model.

```{r removal, echo=T}

require(lme4)
require(car)


model1<-glmer(removal/max ~ habitat+landscape+time+habitat*landscape+(1|finca),data=bi,family=binomial(link="logit"))

Anova(model1)

```

## least square means 
```{r}
require(emmeans)
require(blmeco)

a<-lsmeans(model1, "landscape", type = "response")
a

```


### post-hoc analysis
```{r}
leastsquare = lsmeans(model1, pairwise ~ landscape, adjust="tukey",type="response", alpha =0.05, Letters = letters)
leastsquare


```

